Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-05-11 files/Chapter2/generalvibrationmodel.tex
fixed chapter 2

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}\label{subsec:Timoshenko_Modal_Analsis}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1 as the boundary conditions makes it easy to illustrate the idea of modal analysis. A systematic approach to modal analysis for the Timoshenko beam theory is discussed in Chapter 4.

Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}):
\begin{eqnarray}
	  \partial^2_{x} w - \partial_{x}\phi &=& \partial^{2}_{t} w, \label{eq:1D_Model:ModalPDE1}\\
	  \alpha\partial_{x} w - \alpha\phi + \frac{1}{\gamma}\partial^2_{x}\phi &=&  \partial^{2}_{t} \phi,\label{eq:1D_Model:ModalPDE2}
\end{eqnarray}
with boundary conditions
\begin{eqnarray*}
	w(0,t) = 0, & &	\	 w(1,t) = 0, \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0. \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$. Substituting these trial solutions in \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} yields
\begin{eqnarray*}
	T(t)\tilde{w}''(x) - T(t)\tilde{\phi}'(x) &=& T''(t)\tilde{w}(x),\\
	  \alpha T(t)\tilde{w}'(x) - \alpha T(t)\tilde{\phi}(x) + \frac{1}{\gamma}T(t)\tilde{\phi}''(x) &=&  T''(t)\tilde{\phi}(x).
\end{eqnarray*}
Dividing by $T(t)$,
\begin{eqnarray*}
	\tilde{w}''(x) - \tilde{\phi}'(x) &=& \frac{T''(t)}{T(t)}\tilde{w}(x),\\
	  \alpha \tilde{w}'(x) - \alpha \tilde{\phi}(x) + \frac{1}{\gamma}\tilde{\phi}''(x) &=&  \frac{T''(t)}{T(t)}\tilde{\phi}(x).
\end{eqnarray*}

@@

\subsection{General vibration problem new}
This section is a discussion of a general vibration problem. The discussion will refer to the article \cite{CVV18}. In this article, the authors take damping into consideration, which is not covered in this dissertation. Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.

@@

Therefore $\frac{T''(t)}{T(t)}$ must be a constant. Suppose that $\frac{T''(t)}{T(t)} = -\lambda$. The existence of such a $\lambda$ is uncertain at this point. So we consider the following eigenvalue problem.

@@

Following this result, the authors explain that any $u \in V$, the eigenvector series for $u$ converges to $u$. These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the basis $x_i$. Therefore, for any $u \in V$,
\begin{eqnarray*}
	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i
\end{eqnarray*}

@@

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
\end{flalign}

@@

\subsubsection{Validity of series solution}
Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$? To answer this question, we refer to the article \cite{CVV18}.

@@

In this dissertation, we are trying to compare different models for use in applications. Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.

>>>>

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}\label{subsec:Timoshenko_Modal_Analsis}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1 as the boundary conditions makes it easy to illustrate the idea of modal analysis. A detailed approach to modal analysis for the Timoshenko beam theory is discussed in Chapter 4.

Consider the partial differential equations of a pinned-pinned Timoshenko beam, obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}:
\begin{eqnarray}
	  \partial^2_{x} w - \partial_{x}\phi &=& \partial^{2}_{t} w, \label{eq:1D_Model:ModalPDE1}\\
	  \alpha\partial_{x} w - \alpha\phi + \frac{1}{\gamma}\partial^2_{x}\phi &=&  \partial^{2}_{t} \phi,\label{eq:1D_Model:ModalPDE2}
\end{eqnarray}
with boundary conditions
\begin{eqnarray*} 
	w(0,t) = 0, & &	\	 w(1,t) = 0, \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0. \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$. Substituting these trial solutions in \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} yields
\begin{eqnarray*}
	T(t)\tilde{w}''(x) - T(t)\tilde{\phi}'(x) &=& T''(t)\tilde{w}(x),\\
	  \alpha T(t)\tilde{w}'(x) - \alpha T(t)\tilde{\phi}(x) + \frac{1}{\gamma}T(t)\tilde{\phi}''(x) &=&  T''(t)\tilde{\phi}(x).
\end{eqnarray*}
Dividing by $T(t)$,
\begin{eqnarray*}
	\tilde{w}''(x) - \tilde{\phi}'(x) &=& \frac{T''(t)}{T(t)}\tilde{w}(x),\\
	  \alpha \tilde{w}'(x) - \alpha \tilde{\phi}(x) + \frac{1}{\gamma}\tilde{\phi}''(x) &=&  \frac{T''(t)}{T(t)}\tilde{\phi}(x).
\end{eqnarray*}

@@

\subsection{General vibration problem}
This section is a discussion of a general vibration problem. The discussion will refer to the article \cite{CVV18}. In this article, the authors take damping into consideration, which is not covered in this dissertation.

Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.

@@

Therefore $\displaystyle -\frac{T''(t)}{T(t)}$ must be a non-negative constant. Suppose that $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. The existence of such a $\lambda$ is uncertain at this point. So we consider the following eigenvalue problem.

@@

Following this result, the authors explain that any $u \in V$, the eigenvector series for $u$ converges to $u$. These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the basis $x_i$. Therefore, for any $u \in V$,
\begin{eqnarray*}
	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i.
\end{eqnarray*}

@@

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}\\
	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda_n = 0. \label{lambda_2}
\end{flalign}

@@

\subsubsection{Validity of series solution}
Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$? To answer this question, we can again refer to the article \cite{CVV18}.

@@

In this dissertation, we are trying to compare different models for use in applications. These comparisons are made in Chapter 4 and 6. Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.
